### 2020-12-10 README.Rmd
updated documentation and readme file
updated Fasano Franceschini R Console Output

# fasano.franceschini.test

@@

This is a basic example which shows you how to solve a common problem:

```{r example}
library(fasano.franceschini.test)
## basic example code

sample1Data <- data.frame(x = rnorm(n = 100,mean = 0, sd = 3),
                          y = rnorm(n = 100,mean = 0, sd = 1))
sample2Data <- data.frame(x = rnorm(n = 100,mean = 0, sd = 1),
                          y = rnorm(n = 100,mean = 0, sd = 3))

@@

>>>>

# Fasano Franceschini Test

@@

#### Underlying Distributions Are Different

```{r}
library(fasano.franceschini.test)

#set seed for reproducible example
set.seed(123)

#create 2-D samples with the different underlying distributions
sample1Data <- data.frame(x = rnorm(n = 100,mean = 0, sd = 3),
                          y = rnorm(n = 100,mean = 0, sd = 1))
sample2Data <- data.frame(x = rnorm(n = 100,mean = 0, sd = 1),
                          y = rnorm(n = 100,mean = 0, sd = 3))

@@

#### Underlying Distributions Are The Same

```{r}
#set seed for reproducible example
set.seed(123)

#create 2-D samples with the same underlying distributions
sample1Data <- data.frame(x = rnorm(n = 100,mean = 0, sd = 1),
                          y = rnorm(n = 100,mean = 0, sd = 1))
sample2Data <- data.frame(x = rnorm(n = 100,mean = 0, sd = 1),
                          y = rnorm(n = 100,mean = 0, sd = 1))
